---
title: 'Report Title: Example Report'
author: "Group 3  \nDepartment / Course\n"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    toc: true
    number_sections: true
    toc_depth: 2
fontsize: 11pt
geometry: margin=1in
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{\textit{Short report title}}
- \fancyhead[R]{\leftmark}
- \fancyfoot[C]{\thepage}
- \usepackage{setspace}
- \onehalfspacing
- \usepackage{titling}
- \pretitle{\begin{center}\LARGE\bfseries}
- \posttitle{\end{center}\vspace{1em}}
- \usepackage{caption}
- \captionsetup[figure]{labelfont=bf,textfont=it}
- \captionsetup[table]{labelfont=bf}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.height = 4,
	fig.width = 6,
	message = FALSE,
	warning = FALSE,
	dpi = 150
)
library(knitr)
library(kableExtra)

```

```{r eval=FALSE, message=FALSE, warning=FALSE, code=readLines("Group13code.R"), include=FALSE}
# Do not change this code chunk
source("Group13code.R")
```


# Executive Summary

In the UK it is a criminal offence to drive a motor vehicle with a blood or breath alcohol concentration above the prescribed limit. When a person is arrested for driving under the influence of alcohol it is not usually possible to perform an accurate test of the level of alcohol in the blood or breath immediately. Breath tests can be used as an initial screening tool at the scene, but these are not sufficiently accurate for prosecution. Instead, people are taken to a police station or hospital, where the test can be carried out using proper laboratory protocols. As the body clears alcohol from the blood through time this means that if the individual was over the limit, the measured blood alcohol concentration(BAC) will be lower at the time of measurement than it was when the person was driving a motor vehicle. To deal with this situation, If the BAC after time $t$ (hours) is measured as $C_t$ (g/kg), the BAC at time $0$ is estimated as $C_0 = C_t - βt$, where $\beta$ ($g/kg/h$) is BAC elimination rate. 

The key point is how to find a precise $\beta$ to estimate $C_0$. Forensic scientists currently $2.5\%$ percentile of $\beta$ distribution constructing from samples as the estimated $\beta$ value for every individuals. This method is obviously not rigorous enough for the courts, since:

* The courts will be forced to make decisions under estimated $\beta$ if we only give a single estimation of $beta$, since the calculated $C_0$ is either over or under the legal limit.
* Differences between individuals are ignored, for example age and sex, which may affect $\beta$.
* $\beta$ value at $2.5\%$ is over conservative and most uncertainties are hiding.

In this report, we will introduce a Bayesian regression model with considering the heterogeneity between individuals, the model gives a posterior distribution of $\beta$ by using both samples and prior knowledge. Then we randomly simulate $4000$ $\beta$ values from posterior distribution and find out the probability of the person's BAC over limit while driving. 

In real world, $\beta$ estimation is quite difficult, it depends on the individuals' liver condition, drinking habits, genetic, diet etc. As we don't have corresponding data, in our regression model of $\beta$ is mainly dominate by gender, but we still find some useful variables:
-Gender: Female's BAC elimination rate is larger than male on average, it is explained by liver weight represents a greater fraction of lean body mass in the female gender[2].
-
-

When it is too late to use a blood or breath test and the only information available is eyewitness testimony of the quantity of alcohol consumed. We have to use Widmark's equation:
$$C_t = \frac{A}{Weight \times V_d} - \beta t$$
where $A$ is Amount of Alcohol Consumed (g), $V_d$ is the volume of distribution that need to be found. Forensic scientists use
the same method again to estimate $V_d$ separately with $\beta$. But $V_d$ and $\beta$ are not independent, so we build a joint Bayesian regression model, which can simulate them together to solve with the correlation. Then again after simulation, each $C_t$ is calculated by each pair of $\beta$ and $V_d$, so expert witness can still find a probability of $C_t$ exceeding the limit.

To make it easier, we write the method in a function so other expert witness can also get the results by easily plugging new person's data.


# Motivations: Need improve? Why?
# Disadvantage of current method
1. beta is fixed for all individuals, we need to consider the heterogeneity in individuals.
2. Deviated aim: Police Scotland aims at assessing the probabilities that a person is over the limit, while the parameter beta only concentrates on the range between 2.5% and 97.5%.


# New method: build a linear regression model for beta
Check if age, weight and height have linear relationships with beta.
Or have any patterns?

# Model selection: 
use drop(), look into AIC and R^2


# Hypothesis test(70yr female example-better use 2.5th quantile?): 
H0: C0 < limit, H1: C0 > limit 


# Calculate V_d:
in the Widmark's equation assumption, beta and V_d are independent, so we need to check whether Cov(V_d, beta) = 0


# Further research:
casual effect: biased data selection, 
(e.g. inner correlations between sex and height)


## REPORT
# Exclusive summary
background
Goal - 1, 2, 3
main data + elimination rate explanation
method - model we used
result




# Overview of Datasets
## Variable Description 
- how many observations do we have?
where we get the resourse, reference?
explain each variables in table
## Prelimary analysis 
- initial formula: explain beta60 +  - motivation to improve?

variable correlations? Why?
hypothesis needed? 
why 2.5 quantiles?


# Model selection regarding key variable 'beta60'
## Advantage of current method
simpler model with only one parameter(beta), easier to calculate, suitable for no dataset situations

## New model motivation
Current model disadvantage:
1. beta is fixed for all individuals, we need to consider the heterogeneity in individuals.
2. Deviated aim: Police Scotland aims at assessing the probabilities that a person is over the limit, while the parameter beta only concentrates on the range between 2.5% and 97.5%.




# Bayesian model
intro
New model (Bayesian) 
## Model Selection and Evaluation
- why Bayesian?
Any advantage, any improvement? More accurate? ...
##explanation
###why prior setted?
## how result reflect?



## Model fitting example
How our new model works on the 70 year-old madam?


# Testing another assumption(condition):
## variable explanation
explain all variables we used
explain needed references

##Testing
whether formula reasonable?
whether beta60 relate to Vt? 
how related? 
hows the result? 
how new model fit?


#Limitation
our model limit
data collected reason - cannot reflect the real world
model reason
other reason: variables





#N

Before fitting a Bayesian regression model, appropriate priors need to be specified for all regression coefficients and residual standard deviation. We use weak information priors, allowing the observed data to dominate inference process.The chosen priors are summarised below:

```{r}
priors_table <- tribble(~Parameter, ~Prior,
                        "Regression coefficients (bi)", "Normal(0, 1)",
                        "Residual SD (σ)", "Student-t(3, 0, 5)")

kable(priors_table,
      caption = "Table 1: weak information priors used in the Bayesian regression model")
```

Regression coefficients were assigned Normal(0,1) priors, following the Stan Development Team’s “Prior Choice Recommendations”. For the residual standard deviation we used a half-Student-t prior with 3 degrees of freedom and scale = 5 (σ ∼ t⁺₃(0,5)), following Stan’s recommendations.

#Reference
Stan Development Team. (n.d.). Prior choice recommendations. GitHub. https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations








空腹低 长期饮酒高CTP2E1活性高 性别肝脏大小 药物抑制酒精代谢
测两次血预测beta
如果司机坐在方向盘后面没有被捕，瑞典的交警通常会提交间隔约1小时采集的双重血液样本。假设存在吸收后下降阶段和零阶动力学操作，每个采样时间的平均结果可用于计算酒精的消除率。根据长期调查酒后驾车案件的经验，第一个血液样本通常在逮捕后60分钟获得，这取决于该人被逮捕的全国地点以及是否有医生或护士抽血。
https://www.sciencedirect.com/science/article/pii/S0379073810000770?via%3Dihub

P.Y. Kwo, V.A. Ramchandani, S. O’Connor, D. Amann, L.G. Carr, K. Sandrasegaran, K.K. Kopecky, T.K. Li
Gender differences in alcohol metabolism: relationship to liver volume and effect of adjusting for body mass
Gastroenterology, 115 (1998), pp. 1552-1557