---
title: "Report Title: Example Report"
author: |
  Group 3  
  Department / Course
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    toc: true
    number_sections: true
    toc_depth: 2
fontsize: 11pt
geometry: margin=1in
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\textit{Short report title}}
  - \fancyhead[R]{\leftmark}
  - \fancyfoot[C]{\thepage}
  - \usepackage{setspace}
  - \onehalfspacing
  - \usepackage{titling}
  - \pretitle{\begin{center}\LARGE\bfseries}
  - \posttitle{\end{center}\vspace{1em}}
  - \usepackage{caption}
  - \captionsetup[figure]{labelfont=bf,textfont=it}
  - \captionsetup[table]{labelfont=bf}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
message = FALSE,
warning = FALSE,
fig.width = 6, fig.height = 4,
dpi = 150)
library(knitr)
library(kableExtra)

```

```{r message=FALSE, warning=FALSE, code=readLines("Group13code.R"), include=FALSE}
# Do not change this code chunk
source("Group13code.R")
```


### Advantage of current method
simpler model with only one parameter(beta), easier to calculate, suitable for no dataset situations


# Motivations: Need improve? Why?
# Disadvantage of current method
1. beta is fixed for all individuals, we need to consider the heterogeneity in individuals.
2. Deviated aim: Police Scotland aims at assessing the probabilities that a person is over the limit, while the parameter beta only concentrates on the range between 2.5% and 97.5%.


# New method: build a linear regression model for beta
Check if age, weight and height have linear relationships with beta.
Or have any patterns?
```{r}
beta_reg1 <- data |>
  pivot_longer(
    cols = c(age, weight, height),
    names_to = "variables",
    values_to = "value"
  )

ggplot(beta_reg1, aes(x = value, y = beta)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) + 
  facet_wrap(~ variables, scales = "free_x") +
  theme_minimal()
 
```
# Model selection: 
use drop(), look into AIC and R^2


# Hypothesis test(70yr female example-better use 2.5th quantile?): 
H0: C0 < limit, H1: C0 > limit 


# Calculate V_d:
in the Widmark's equation assumption, beta and V_d are independent, so we need to check whether Cov(V_d, beta) = 0


# Further research:
casual effect: biased data selection, 
(e.g. inner correlations between sex and height)


## REPORT
# Exclusive summary
background
Goal - 1, 2, 3
main data + elimination rate explanation
method - model we used
result




# Dataset- in table
Description - how many observations do we have?
where we get the resourse, reference?
explain each variables in table
Prelimary analysis - initial formula: explain beta60 +  - motivation to improve?

variable correlations? Why?
hypothesis needed? 
why 2.5 quantiles?


# Model selsction - why Baysian?
Any advantage, any improvement? More accurate? 

# How model works on the 70 year-old madam
explanation
why prior setted?
how result reflect?

# Testing another assumption(condition):
explain all variables we used
explain needed references
whether formula reasonable?
whether beta0 relate to Vt? 
how related? 
hows the result? 
how new model fit?


#Limitation
our model limit
data collected reason - cannot reflect the real world
model reason
other reason









